---
# title: "Combined Serial Interval Distributions"
# author: "Amy Gimma"
# date: "3/19/2020"
output: html_document
---

## Combining Serial Interval Distributions 

Documentation to come...

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load Packages
library(tidyverse)
library(googlesheets4)
library(openxlsx)
library(magrittr)
library(kableExtra)

# set seed
set.seed(20200319)
```


```{r create_study_intervals}
####generate serial interval sample
serial <- read.csv("nCoV_Serial.csv")
serial <- serial %>% mutate(x = round(x,1))
serial[1,2] <- 0

serial_freq <- seq(0,21,by = 0.1) %>% 
  enframe %>% 
  left_join(., serial, by = c("value" = "x")) %>% 
  distinct() %>% 
  mutate(Curve2 = imputeTS::na_interpolation(Curve1)) %>%
  mutate(tot = sum(Curve2)) %>%
  mutate(prop = Curve2/tot) %>%
  mutate(n = round(prop*n())) 



serial_sample_Li <- list()
for(i in 1:nrow(serial_freq)){
  serial_sample_Li[[i]] <- rep(serial_freq$value[i], serial_freq$n[i])
}

serial_sample_Li %<>% unlist
# density(serial_sample_Li, bw = 0.2) %>% plot
median(serial_sample_Li)
quantile(serial_sample_Li, c(0.025,0.5, 0.975))


# Load data from Bi et al. (2020)
# Epidemiology and Transmission of COVID-19 in Shenzhen China: Analysis of 391
# cases and 1,286 of their close contacts.

n = length(serial_sample_Li)
# Overall
# Incubation Period, lognormal distribution
# parameter 1: mean = 1.57, CI = 1.44-1.69
# parameter2: mean = 0.65, CI = 0.56, 0.73
# mean = 5.95, 4.94-7.11
param1 <- 1.57
param2 <- 0.65
incubation_sample_Bi <- list()
incubation_sample_Bi <- sort(round(rlnorm(n, param1, param2), 1))

incubation_sample_Bi %>% mean
incubation_sample_Bi %>% log %>% sd
quantile(incubation_sample_Bi, c(0.025,0.975))

# Serial Interval, gamma distribution
# parameter 1: mean = 2.29, CI = 1.77-3.34
# parameter 2: mean = 0.36, CI = 0.26-0.57
param1 <- 2.29
param2 <- 0.36
serial_sample_Bi <- list()
serial_sample_Bi[["all"]] <- sort(round(rgamma(n, param1, param2), 1))
serial_sample_Bi[["early"]] <-  sort(round(rnorm(n, 3.6, 0.6), 1))
# serial_sample_Bi[["mid"]] <-  rnorm(n, 8.1, 2.9) %>% 
#   round(., 1) %>% 
#   sort
# serial_sample_Bi[["late"]] <-  rnorm(n, 8, 1.7) %>% 
#   round(., 1) %>% 
#   sort

mean(serial_sample_Bi$all)
quantile(serial_sample_Bi$all, c(0.025, 0.5, 0.975))

median(serial_sample_Bi$early)
quantile(serial_sample_Bi$early, c(0.025, 0.5, 0.975))


# Load data from Nishiura, Linton, Akhmgitetzhanov (2020)
# parameter 1: mean = 2.305, sd = 0.439
# parameter 2: mean = 5.452, sd = 0.674
param1 <- 2.305
param2 <- 5.452
serial_sample_Nishiura <- sort(round(rweibull(n, param1, param2), 1)) 

median(serial_sample_Nishiura)
quantile(serial_sample_Nishiura, c(0.025, 0.5, 0.975))


serial_dists <- data.frame(
  bi_all = serial_sample_Bi$all,
  bi_early = serial_sample_Bi$early,
  # bi_mid = serial_sample_Bi$mid,
  # bi_late = serial_sample_Bi$late,
  li = serial_sample_Li,
  nishiura = serial_sample_Nishiura
) %>% gather(key = "distribution_name", "days")

summary(serial_dists)
```




```{r plot_study_serials}
# Plot all
ggplot(serial_dists, aes(x = days)) +
  geom_density(color = "darkred", fill = "darkred", alpha = 0.4) +
  ggtitle("Serial Distribution Density - all data") +
  xlab("Days") + ylab("Density")

# Plot by distribution
ggplot(serial_dists, aes(x = days)) +
  geom_density(color = "darkred", fill = "darkred", alpha = 0.4) +
  facet_grid(vars(distribution_name), scales = "free") +
  ggtitle("Serial Distribution Density Plots") +
  xlab("Days") + ylab("Density") + theme_bw()

early_dists <- c("bi_early", "li", "nishiura")
early_serial <- serial_dists %>%
  filter(distribution_name %in% early_dists)

ggplot(early_serial, aes(x = days)) +
  geom_density(color = "steelblue4", fill = "steelblue4", alpha = 0.4) +
  ggtitle("Serial Distribution Density - all data") +
  xlab("Days") + ylab("Density") +
  theme_bw()

# Plot by distribution
ggplot(early_serial, aes(x = days)) +
  geom_density(color = "steelblue4", fill = "steelblue4", alpha = 0.4) +
  facet_grid(vars(distribution_name), scales = "free") +
  ggtitle("Serial Distribution Density Plots") +
  scale_x_continuous(breaks = seq(0,25,2), limits = c(0, 20)) +
  xlab("Days") + ylab("Density") + theme_bw()

summary(early_serial)

```

```{r create_fitted}
fit_gamma <- fitdistrplus::fitdist(early_serial$days, "gamma",
                                   optim.method = "Nelder-Mead")
fit_weibull <- fitdistrplus::fitdist(early_serial$days, "weibull",
                                     optim.method = "Nelder-Mead")

gamma_dist <- rgamma(10000, shape = fit_gamma$estimate["shape"],
                     rate = fit_gamma$estimate["rate"])

weibull_dist <- rweibull(10000, shape = fit_weibull$estimate["shape"],
                     scale = fit_weibull$estimate["scale"])

fitted_dists <- data.frame(Gamma = gamma_dist, Weibull = weibull_dist) %>%
  gather(key = "distribution", value = "days")

```

## Create and assess fitted distributions
```{r plot_fits}
plot(fit_gamma)
summary(fit_gamma)
# descdist(gamma_dist, boot = 1000)

# bfg <- bootdist(bfg)
# plot(bfg)
# summary(bfg)

plot(fit_weibull)
summary(fit_weibull)
# descdist(weibull_dist, boot = 1000)

# bfw <- bootdist(bfw)
# plot(bfw)
# summary(bfw)
```


## Plot fitted distributions
(combined distributions from Li et al., Bi et al. (early), Nishiura et al.)


```{r plot_fitted}

ggplot(fitted_dists, aes(x = days)) +
  geom_density(aes(color = distribution, fill = distribution), alpha = 0.3) +
  ggtitle("Fitted Distributions - Early Serial Interval estimates")


by(fitted_dists$days,fitted_dists$distribution, summary)
```

```{r params_table}
fits <- list(fit_gamma, fit_weibull)

param_table <- data.frame(
  distribution = c("gamma", "weibull"),
  param_1_name = vapply(fits, function(x) { names(x$estimate)[1]}, FUN.VALUE = c("1")),
  param_1_value = vapply(fits, function(x) { x$estimate[1]}, FUN.VALUE = c(1)),
  param_1_sd = vapply(fits, function(x) { x$sd[1]}, FUN.VALUE = c(1)),
  param_name_2 = vapply(fits, function(x) { names(x$estimate)[2]}, FUN.VALUE = c("1")),
  param_value_2 = vapply(fits, function(x) { x$estimate[2]}, FUN.VALUE = c(1)),
  param_2_sd = vapply(fits, function(x) { x$sd[2]}, FUN.VALUE = c(1))
)

```

### Parameter table
```{r show_params_table}
param_table %>% kable(digits = 4) %>% kable_styling(full_width = FALSE)
```

### Download distribution csv files (from github repo)
(combined distributions from Li et al., Bi et al. (early), Nishiura et al.)

* [Gamma distribution csv](https://github.com/amygimma/2019nCoV_proportion_asym/blob/outputs/gamma_fitted_early_serial_dists.csv)
* [Weibull distribution csv](https://github.com/amygimma/2019nCoV_proportion_asym/blob/outputs/weibull_fitted_early_serial_dists.csv)


